Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-02-05 presub/coverletter.tex
As sumbitted.

% Cover letter using letter.cls
\documentclass[11pt]{letter} % Uses 10pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:

\topmargin=-1.5in    % Make letterhead start about 1 inch from top of page 
\textheight=11.75in    % text height can be bigger for a longer letter
\oddsidemargin=0pt   % leftmargin is 1 inch
\textwidth=6.5in     % textwidth of 6.5in leaves 1 inch for right margin
\usepackage{url}
\usepackage{hyperref}
\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
}
\usepackage{graphicx}
\usepackage[strict]{changepage}
\usepackage{xcolor}

%--------------------------------------------------------------
% A few colors for hyperlinks.
%--------------------------------------------------------------
\definecolor{plum}{rgb}{0.36078, 0.20784, 0.4}
\definecolor{chameleon}{rgb}{0.30588, 0.60392, 0.023529}
\definecolor{cornflower}{rgb}{0.12549, 0.29020, 0.52941}
\definecolor{scarlet}{rgb}{0.8, 0, 0}
\definecolor{brick}{rgb}{0.64314, 0, 0}

\newcommand{\email}[1]{\href{mailto:#1}{\tt \textcolor{cornflower}{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left

\nopagebreak  
\begin{letter}
{Leslie Sage \\
l.sage@us.nature.com \\}

{
\leftskip = 0pt plus 1 fill
\rightskip = 0pt
\parindent 0pt
%\obeylines
%
%
{{\bf Dr Will M. Farr}} \\
School of Physics and Astronomy\\
University of Birmingham\\
Birmingham, B15 2TT\\
United Kingdom\\
 \url{w.farr@bham.ac.uk} \\

}

\begin{minipage}[c]{5in}\vskip-4.25cm
\begin{flushleft}
	\begin{minipage}[c]{3cm}
		\begin{flushleft}
			\includegraphics*[width=8cm]{birmingham_logo.png}%
		\end{flushleft}
	\end{minipage}
\end{flushleft}
\end{minipage}

\opening{Dear Leslie,}

\noindent I submit for your consideration a Letter on the ``Detection of Oscillations in Aldebaran with Ground-Based Observations''.

@@

One astronomer's noise is another astronomer's data: we have found that the noise in these archival observations is actually the signal of stellar oscillations. With radical new data processing techniques, we have re-analysed historical RV data and confirmed our result with new observations. Using our Gaussian Process model we detect the signal of stellar oscillations, missed by previous authors, and consequently infer much more accurate orbital parameters for the planet. This technique will be widely applicable to legacy and future datasets, allowing both asteroseismology with RV, and also searches for lower-mass companions to giants than was previously possible.

We have also independently confirmed our results with new photometry from the \emph{Kepler}-2 (K2) mission, again using a highly novel algorithm to extract a precise light curve of the brightest star ever observed by \emph{Kepler}. The K2 light curve shows very clear oscillations that are in perfect agreement with the frequency we infer from RV.

With asteroseismology we constrain the star's age for the first time, measure its mass with a factor of two better precision than had previously been possible (to 6\%), and consequently obtain the mass of the giant planet to a precision of 12\%.

@@

Thank you for considering our submission. Please do not hesitate to contact me with any questions.\\

\closing{Yours sincerely, \\
\vspace{1.0cm}
Will Farr}

%\encl{One paragraph Letter outline}					% Enclosures

>>>>

\documentclass{letter}
\usepackage{url}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\signature{Will Farr}

\address{Will M. Farr\\School of Physics and Astronomy\\University of Birmingham\\Birmingham\\B15 2TT\\United Kingdom}

\begin{letter}
{Leslie Sage \\
l.sage@us.nature.com \\}

\opening{Dear Dr. Sage:}

Please find enclosed a submission for a Nature Letter titled ``Aldebaran~b's
temperate past uncovered in planet search data''.

@@

One astronomer's noise is another astronomer's data: using new data processing
techniques, we have found that some of the ``noise'' in these archival
observations is actually the signal of stellar oscillations. We confirmed our
result with new observations. The asteroseismic oscillations allow us to infer
much more accurate stellar parameters and therefore orbital parameters for the
planet; we constrain the star's age, measure its mass with a factor of two
better precision than had previously been possible (to 6\%), and consequently
obtain the mass of the giant planet to a precision of 12\%.

Our technique will be widely applicable to legacy and future datasets, allowing
both asteroseismology with RV, and also searches for lower-mass companions to
giants than was previously possible.  There are many targets with \emph{already
existing} archival data amenable to this technique, and it will also be
applicable to upcoming and ongoing large surveys (Gaia, LSST, etc).

We have also independently confirmed our results with new photometry from the
\emph{Kepler}-2 (K2) mission, again using a novel algorithm to extract a precise
light curve of the brightest star ever observed by \emph{Kepler}. The K2 light
curve shows very clear oscillations that are in agreement with the frequency we
infer from RV.

@@

Should you be interested in publishing the paper in Nature, it will require some
minor reformatting.  It is currently about 3000 words in the main body, with
five display items; however many details currently in the main body can be
easily moved to the appendices / methods sections.  It also contains more
references than permitted in a Letter, but many of these can also be moved to
the Methods section and others can be eliminated if necessary.

Thank you for considering our submission. Please do not hesitate to contact me
with any questions.  Should you feel that our submission is not appropriate for
Nature, we would be happy to have it considered for Nature Astronomy.

\closing{Sincerely,}
